LLM-Driven CIDOC-CRM Knowledge Graph Extraction from Museum Archives

### 2025-05-04 paper/paper.tex
paper: small addition to abstract

    Evaluation results show that larger models (e.g., DeepSeek R1) are capable of high ontology conformance (up to 98.73\%) while smaller models struggle. While all generated KGs improved KBQA performance over a no-context baseline, the ontology-guided approach showed limited and mixed impact on KBQA accuracy compared to the ontology-free graphs in our setup. This research underscores the potential of LLMs for generating ontology-conformant KGs within the cultural heritage domain and highlights the need for more sophisticated evaluation benchmarks to assess CIDOC-CRM KG generation methods.
\end{abstract}

>>>>

    Evaluation results show that larger models (e.g., DeepSeek R1) are capable of high ontology conformance (up to 98.73\%) while smaller models struggle to reach 50\% conformance. While all generated KGs improved KBQA performance over a no-context baseline, the ontology-guided approach showed limited and mixed impact on KBQA accuracy compared to the ontology-free graphs in our setup. This research underscores the potential of LLMs for generating ontology-conformant KGs within the cultural heritage domain and highlights the need for more sophisticated evaluation benchmarks to assess CIDOC-CRM KG generation methods.
\end{abstract}
